---
title: "Analysis for Troops and Development Projects in Latin America"
format:
  html:
    highlight: tango
    theme: spacelab
    toc: true
    toc_float: true
    toc_collapsed: true
    code_folding: show
    number_sections: true
    fig_width: 6
    fig_height: 4
    fig_caption: true
    dpi: 400
    df_print: paged
    keep_md: true
    self_contained: false
editor_options: 
  chunk_output_type: console
---

## Setup 

```{r setup}
#pak::pak("vdeminstitute/vdemdata")
#pak::pak("meflynn/flynnprojects")


library(tidyverse)
library(countrycode)
library(brms)
library(projpred)
library(ggdist)
library(tidybayes)
library(ggdist)
library(ggrepel)
library(ggtext)
library(peacesciencer)
library(troopdata)
library(modelsummary)
library(tinytable)
library(kableExtra)
library(rnaturalearth)
library(flynnprojects)
#library(vdemdata)
library(stringr)
library(here)
library(marginaleffects)
library(lme4)
library(scales)
library(CoordinateCleaner)
library(patchwork)
library(projpred)
library(future)

sysfonts::font_add_google("Oswald", "oswald")
showtext::showtext_auto()
showtext::showtext_opts(dpi = 400)

set.seed(65502)

```





# Create Data Set for Analysis

```{r data-setup}
#| echo: false
#| message: false
#| warning: false



# Clean exports to US IMF data
exports.to.us <- readr::read_csv(here::here("Data/Raw Data/imf-dots/Imports_from_Counterpart_Countries.csv")) |> 
  dplyr::rename("country" = "COUNTERPART_COUNTRY") |> 
  dplyr::filter(!is.na(country)) |> 
  dplyr::mutate(ccode = countrycode::countrycode(country, origin = "country.name",  destination = "cown"),
                region = countrycode(ccode, origin = "cown", destination = "region")) |> 
  dplyr::rename("year" = "TIME_PERIOD", "exports_to_us" = "OBS_VALUE") |> 
  dplyr::select(country, ccode, region, year, exports_to_us) |> 
  dplyr::group_by(country) |> 
  dplyr::mutate(exports_to_us = as.numeric(exports_to_us)) |> 
  dplyr::filter(year >= 2000)


# Clean imports from US IMF data
imports.from.us <- readr::read_csv(here::here("Data/Raw Data/imf-dots/Exports_to_Counterpart_Countries.csv")) |> 
  dplyr::rename("country" = "COUNTERPART_COUNTRY") |> 
  dplyr::filter(!is.na(country)) |> 
  dplyr::mutate(ccode = countrycode::countrycode(country, origin = "country.name",  destination = "cown"),
                region = countrycode(ccode, origin = "cown", destination = "region")) |> 
  dplyr::rename("year" = "TIME_PERIOD", "imports_from_us" = "OBS_VALUE") |> 
  dplyr::select(country, ccode, region, year, imports_from_us) |> 
  dplyr::group_by(country) |> 
  dplyr::mutate(imports_from_us = as.numeric(imports_from_us)) |> 
  dplyr::filter(year >= 2000)


options(digits = 3)
# Health Data from World Bank WDI
health.data <- readxl::read_xlsx(here::here("Data/Raw Data/P_Data_Extract_From_Health_Nutrition_and_Population_Statistics/P_Data_Extract_From_World_Development_Indicators.xlsx")) |> 
  dplyr::filter(!is.na(`Series Code`)) |> 
  dplyr::rename("variable" = 1, "country" = 3) |> 
  pivot_longer(cols = c(5:29)) |> 
  group_by(country) |> 
  dplyr::mutate(name = as.numeric(str_extract(name, "\\d{4} ")),
                value = case_when(
                  grepl("\\.\\.", value) ~ NA,
                  TRUE ~ round(as.numeric(value), 3)
                )) |> 
  dplyr::rename("year" = "name") |> 
  ungroup() |> 
  dplyr::mutate(ccode = countrycode(variable,
                                    origin = "country.name",
                                    destination = "cown")) |>
  pivot_wider(id_cols = c("variable", "ccode", "year"),
              names_from = "country",
              values_from = "value") |>
  dplyr::rename("country" = "variable",
                "infant_deaths_num" = `Number of infant deaths`,
                "infant_mortality" = `Mortality rate, infant (per 1,000 live births)`,
                "infant_mortality_female" = `Mortality rate, infant, female (per 1,000 live births)`,
                "infant_mortality_male" = `Mortality rate, infant, male (per 1,000 live births)`,
                "hospital_beds_per_1000" = `Hospital beds (per 1,000 people)`,
                "healthcare_expenditures_pc" = `Current health expenditure per capita (current US$)`,
                "healthcare_expenditures" = `Current health expenditure (% of GDP)`,
                "healthcare_expenditures_gov" = `Domestic general government health expenditure (% of GDP)`,
                "healthcare_expenditures_gov_pc" = `Domestic general government health expenditure (% of current health expenditure)`,
                "material_mortality_ratio_modeled" = `Maternal mortality ratio (modeled estimate, per 100,000 live births)`,
                "material_mortality_ratio" = `Maternal mortality ratio (national estimate, per 100,000 live births)`,
                "population_growth" = `Population growth (annual %)`,
                "unemployment_rate" = `Unemployment, total (% of total labor force) (national estimate)`,
                "trade_gdp" = `Trade (% of GDP)`,
                "gdp_constant" = `GDP (constant 2015 US$)`,
                ) |> 
  dplyr::select(ccode, year, everything()) |> 
  dplyr::filter(!is.na(ccode))


# Health Data Addendum
health.data.2 <- read_csv(here::here("Data/Raw Data/P_Data_Extract_From_Health_Nutrition_and_Population_Statistics/8efd2565-8927-4877-a42a-9c6ebee02db2_Data.csv")) |> 
  dplyr::filter(!is.na(`Series Code`)) |> 
  dplyr::rename("variable" = 1, "country" = 3) |> 
  pivot_longer(cols = c(5:29)) |> 
  group_by(country) |> 
  dplyr::mutate(name = as.numeric(str_extract(name, "\\d{4} ")),
                value = case_when(
                  grepl("\\.\\.", value) ~ NA,
                  TRUE ~ round(as.numeric(value), 3)
                )) |> 
  dplyr::rename("year" = "name") |> 
  ungroup() |> 
  dplyr::mutate(ccode = countrycode(country,
                                    origin = "country.name",
                                    destination = "cown")) |>
  pivot_wider(id_cols = c("country", "ccode", "year"),
              names_from = "variable",
              values_from = "value") |> 
  dplyr::rename("hospital_beds" = `Hospital beds (per 1,000 people)`,
                "infant_mortality_rate" = `Mortality rate, infant (per 1,000 live births)`,
                "infant_mortality_rate_female" = `Mortality rate, infant, female (per 1,000 live births)`,
                "infant_mortality_rate_male" = `Mortality rate, infant, male (per 1,000 live births)`,
                "infant_deaths_num" = `Number of infant deaths`,
                "population_total" = `Population, total`,
                "education_spending" = `Public spending on education, total (% of GDP)`,
                "population_rural" = `Rural population (% of total population)`,
                "population_urban" = `Urban population (% of total population)`
  )
  


# Homicide Data
# Rate per 100,000 people. Both sexes.
homicide.data <- readr::read_csv(here::here("Data/WHO/homicide-data.csv")) |> 
  dplyr::mutate(ccode = countrycode::countrycode(Location, origin = "country.name", destination = "cown"),
                homicide_rate = FactValueNumeric,
                year = Period) |> 
  dplyr::filter(Dim1 == "Both sexes") |> 
  dplyr::select(ccode, year, homicide_rate)

# Iraq Contributions
iraq.contributions <- readxl::read_xlsx(here::here("Data/Raw Data/Iraq Coalition Contributions.xlsx")) |> 
  dplyr::mutate(ccode = countrycode::countrycode(country, origin = "country.name", destination = "cown")) |>
  dplyr::mutate(iraq_coalition = 1,
                beginyear = as.Date(beginyear),
                endyear = as.Date(endyear)) |> 
  rowwise() |> 
  dplyr::mutate(time = list(lubridate::year(beginyear):lubridate::year(endyear))) |> 
  tidyr::unnest(time) |> 
  dplyr::select(country, ccode, time, iraq_coalition, dead, wounded, troopstotal, troopspeak) |>
  dplyr::mutate(across(c(dead, wounded, troopstotal, troopspeak),
                       ~ as.numeric(.x))) |> 
  dplyr::rename("year" = "time")

# Create ccode list for more general Iraq coalition of the willing dummy variable.
iraq.ccode.list <- unique(iraq.contributions$ccode)

# V-Dem Data
vdem.data <- vdemdata::vdem  |> 
  dplyr::filter(year >= 1999) |> 
  dplyr::select(country_name, COWcode, year, v2x_polyarchy, v2x_libdem) |> 
  dplyr::rename("ccode" = COWcode, "country" = country_name)


#  UN Voting data
un.data <- read_csv(here::here("Data/Raw Data/IdealpointestimatesAll_Jun2024.csv")) |> 
  dplyr::mutate(year = session + 1945) |> 
  dplyr::filter(year>=1999) |>
  group_by(year) |> 
  dplyr::mutate(US_Idealpoint = IdealPointAll[ccode==2],
                un_distance_abs = abs(US_Idealpoint - IdealPointAll),
                un_distance = US_Idealpoint - IdealPointAll) |> 
  dplyr::select(year, ccode, USAgree, un_distance) 


# Database of Political Institutions
iadb.data <- readr::read_csv(here::here("Data/Raw Data/the-database-of-political-institutions-dpi-2023-2026-08-26-01-52/DPI 2023 (CSV Version)/DPI 2023 CSV Version.csv")) |> 
  dplyr::mutate(year = str_extract(year, 
                                   pattern = "^\\d{4}"),
                year = as.numeric(year),
                ccode = countrycode::countrycode(countryname,
                                                 origin = "country.name",
                                                 destination = "cown"),
                execrlc = factor(execrlc,
                                 levels = c("Left", "Center", "Right")),
                execrlc_num = case_when(
                  execrlc == "Left" ~ -1,
                  execrlc == "Center" ~ 0,
                  execrlc == "Right" ~ 1,
                  TRUE ~ NA
                )) |> 
  dplyr::mutate(
    us_exec_party_code = case_when(
      year >= 1998 & year <= 2000 ~ -1,  # Clinton (D)
      year >= 2001 & year <= 2008 ~  1,  # Bush (R)
      year >= 2009 & year <= 2016 ~ -1,  # Obama (D)
      year >= 2017 & year <= 2020 ~  1,  # Trump (R)
      year >= 2021 & year <= 2024 ~ -1,  # Biden (D)
      TRUE ~ NA_real_
    ),
    executive_difference = execrlc_num - us_exec_party_code,
    executive_alignment = case_when( # Dummy to indicate if parties are roughly the same
      execrlc_num == us_exec_party_code ~ 1,
      TRUE ~ 0
    )) |> 
  dplyr::select(countryname, ccode, year, execrlc, executive_difference, execrlc_num, executive_alignment, us_exec_party_code)



# DHS Immigration Data for 2009
# Asylum grants
dhs.2009.asylum <- readxl::read_xls(here::here("Data/Raw Data/DHS Immigration Data/RFA2009_0/table17d.xls"), skip = 14) |> 
  dplyr::mutate(ccode = countrycode::countrycode(Total, origin = "country.name", destination = "cown")) |> 
  dplyr::rename("countryname" = "Total") |> 
  tidyr::pivot_longer(cols = 2:11) |> 
  group_by(countryname) |> 
  dplyr::mutate(year = seq(2000,2009)) |> 
  dplyr::mutate(value = as.numeric(value)) |> 
  dplyr::rename("asylum_grants" = "value")

# Refugee grants
dhs.2009.refugee <- readxl::read_xls(here::here("Data/Raw Data/DHS Immigration Data/RFA2009_0/table14d.xls"), skip = 14) |> 
  dplyr::mutate(ccode = countrycode::countrycode(Total, origin = "country.name", destination = "cown")) |> 
  dplyr::rename("countryname" = "Total") |> 
  tidyr::pivot_longer(cols = 2:11) |> 
  group_by(countryname) |> 
  dplyr::mutate(year = seq(2000,2009)) |> 
  dplyr::mutate(value = as.numeric(value)) |> 
  dplyr::rename("refugee_grants" = "value")

# DHS Immigration Data for 2019
# Asylum grants
dhs.2019.asylum <- readxl::read_xlsx(here::here("Data/Raw Data/DHS Immigration Data/yrbk_2019_rfa_excel_final/fy2019_table17d.xlsx"), skip = 14) |> 
  dplyr::mutate(ccode = countrycode::countrycode(Total, origin = "country.name", destination = "cown")) |> 
  dplyr::rename("countryname" = "Total") |> 
  tidyr::pivot_longer(cols = 2:11) |> 
  group_by(countryname) |> 
  dplyr::mutate(year = seq(2010,2019)) |> 
  dplyr::mutate(value = as.numeric(value)) |> 
  dplyr::rename("asylum_grants" = "value")

# Asylum grants
dhs.2019.refugee <- readxl::read_xlsx(here::here("Data/Raw Data/DHS Immigration Data/yrbk_2019_rfa_excel_final/fy2019_table14d.xlsx"), skip = 14) |> 
  dplyr::mutate(ccode = countrycode::countrycode(Total, origin = "country.name", destination = "cown")) |> 
  dplyr::rename("countryname" = "Total") |> 
  tidyr::pivot_longer(cols = 2:11) |> 
  group_by(countryname) |> 
  dplyr::mutate(year = seq(2010,2019)) |> 
  dplyr::mutate(value = as.numeric(value)) |> 
  dplyr::rename("refugee_grants" = "value")

# DHS Immigration Data for 2019
# Asylum grants
dhs.2023.asylum <- readxl::read_xlsx(here::here("Data/Raw Data/DHS Immigration Data/2023_0818_plcy_yearbook_refugees_and_asylees_fy2022_0.xlsx"), sheet = "Table 17d", skip = 16) |> 
  dplyr::mutate(ccode = countrycode::countrycode(Total, origin = "country.name", destination = "cown")) |> 
  dplyr::rename("countryname" = "Total") |> 
  tidyr::pivot_longer(cols = 2:11) |> 
  group_by(countryname) |> 
  dplyr::mutate(year = seq(2013,2022)) |> 
  dplyr::mutate(value = as.numeric(value)) |> 
  dplyr::filter(year > 2019) |> 
  dplyr::rename("asylum_grants" = "value")


# Refugee grants
dhs.2023.refugee <- readxl::read_xlsx(here::here("Data/Raw Data/DHS Immigration Data/2023_0818_plcy_yearbook_refugees_and_asylees_fy2022_0.xlsx"), sheet = "Table 14d", skip = 16) |> 
  dplyr::mutate(`84989` = as.character(`84989`),
                ccode = countrycode::countrycode(Total, origin = "country.name", destination = "cown")) |> 
  dplyr::rename("countryname" = "Total") |> 
  tidyr::pivot_longer(cols = 2:11) |> 
  group_by(countryname) |> 
  dplyr::mutate(year = seq(2013,2022)) |> 
  dplyr::mutate(value = as.numeric(value)) |> 
  dplyr::filter(year > 2019) |> 
  dplyr::rename("refugee_grants" = "value")

# Bind data together
asylum.data.combined <- bind_rows(dhs.2009.asylum, dhs.2019.asylum, dhs.2023.asylum) |> 
  dplyr::mutate(region = countrycode(countryname, 
                                     origin = "country.name", 
                                     destination = "region")) |> 
  dplyr::filter(region == "Latin America & Caribbean") |> 
  dplyr::select(countryname, ccode, year, region, asylum_grants) |> 
  dplyr::select(-region) |> 
  left_join(dhs.2009.refugee) |> 
  left_join(dhs.2019.refugee) |> 
  left_join(dhs.2023.refugee) |> 
  dplyr::mutate(refugee_grants = case_when(
    is.na(refugee_grants) ~ 0,
    TRUE ~ refugee_grants
  ),
  asylum_refugee_total = asylum_grants + refugee_grants) |> 
  dplyr::select(-name)


# BTH/NH Deployment Indicator
deployment.indicator <- readxl::read_xlsx(here::here("Data/SOUTHCOM Data/BTH History.xlsx")) |> 
  group_by(Country, Year) |>
  dplyr::summarise(deployment = 1) |>
  ungroup() |> 
  dplyr::mutate(ccode = countrycode::countrycode(sourcevar = Country, 
                                                 origin = "country.name", 
                                                 destination = "cown")) |> 
  dplyr::rename("year" = "Year")

# Homicide Data


# Centroid data for country capitals
centroid.df <- CoordinateCleaner::countryref |> 
  dplyr::mutate(ccode = countrycode::countrycode(sourcevar = iso3, 
                                                  origin = "iso3c", 
                                                  destination = "cown")) |> 
  dplyr::filter(type == "country") |> 
  dplyr::group_by(ccode) |> 
  dplyr::filter(!is.na(ccode)) |> 
  dplyr::summarise(ccode = first(ccode),
                   capital.lon = first(capital.lon), 
                   capital.lat = first(capital.lat)) 


data.analysis <- peacesciencer::create_stateyears(system = "cow", subset_years = c(1998:2024)) |> 
  dplyr::mutate(region = countrycode::countrycode(sourcevar = ccode, 
                                                  origin = "cown", 
                                                  destination = "region")) |> 
  dplyr::filter(region == "Latin America & Caribbean") |> 
  left_join(health.data, by = c("ccode", "year")) |>
  left_join(health.data.2, by = c("ccode", "year")) |> 
  left_join(vdem.data, by = c("ccode", "year")) |> 
  left_join(iadb.data, by = c("ccode", "year")) |> 
  left_join(exports.to.us, by = c("ccode", "year")) |>
  left_join(imports.from.us, by = c("ccode", "year")) |>
  left_join(un.data, by = c("ccode", "year")) |>
  left_join(deployment.indicator, by = c("ccode", "year")) |> 
  left_join(iraq.contributions, by = c("ccode", "year")) |>
  left_join(homicide.data, by = c("ccode", "year")) |> 
  left_join(asylum.data.combined, by = c("ccode", "year")) |> 
  left_join(centroid.df, by = "ccode") |>
  dplyr::rename("countryname" = "cw_name") |> 
  mutate(deployment = case_when(
    is.na(deployment) ~ 0, 
    TRUE ~ deployment),
    alba_member = case_when(
      str_detect(countryname, "Venezuela") & year >= 2004 ~ 1,
      str_detect(countryname, "Cuba") & year >= 2004 ~ 1,
      str_detect(countryname, "Nicaragua") & year >= 2007 ~ 1,
      str_detect(countryname, "Bolivia") & year >= 2006 ~ 1,
      str_detect(countryname, "Ecuador") & year >= 2007 & year <= 2018 ~ 1,
      str_detect(countryname, "Honduras") & year >= 2008 & year <= 2009 ~ 1,
      str_detect(countryname, "Dominica") & year >= 2008 ~ 1,
      str_detect(countryname, "Antigua") & year >= 2009 ~ 1,
      str_detect(countryname, "St. Vincent") & year >= 2009 ~ 1,
      str_detect(countryname, "St. Kitts") & year >= 2014 ~ 1,
      str_detect(countryname, "Grenada") & year >= 2014 ~ 1,
      str_detect(countryname, "St. Lucia") & year >= 2013 ~ 1,
      TRUE ~ 0
    ),
    asylum_grants = case_when(
      is.na(asylum_grants) ~ 0,
      TRUE ~ asylum_grants
    ),
    refugee_grants = case_when(
      is.na(refugee_grants) ~ 0,
      TRUE ~ refugee_grants
    ),
    asylum_refugee_total = case_when(
      is.na(asylum_refugee_total) ~ 0,
      TRUE ~ asylum_refugee_total
    ),
    gdppc = gdp_constant/population_total) |> # Ensure inflation adjusted
  group_by(ccode) |> 
  dplyr::mutate(deployment_cumsum = cumsum(deployment),
                deployment_lead_1 = dplyr::lead(deployment, n = 1L),
                deployment_lead_2 = dplyr::lead(deployment, n = 2L)) |>
  group_by(ccode, deployment_cumsum) |> 
  dplyr::mutate(time_since_deployment = seq_along(deployment_cumsum) - 1) |>
  ungroup() |> 
  dplyr::mutate(across(c(exports_to_us, imports_from_us, v2x_polyarchy, gdp_constant, gdppc, infant_mortality_rate, population_total, population_urban, education_spending, healthcare_expenditures, population_rural, un_distance, USAgree, unemployment_rate, time_since_deployment, homicide_rate, asylum_grants, refugee_grants, asylum_refugee_total), 
                       ~arm::rescale(.x),
                       .names = "{.col}_z"),
                across(c(exports_to_us, imports_from_us, gdppc, gdp_constant, population_total, infant_mortality_rate),
                       ~log(.x),
                       .names = "log_{.col}")) |>
  dplyr::mutate(across(c(iraq_coalition, dead, wounded, troopstotal, troopspeak),
                       ~ case_when(
                         is.na(.x) ~ 0,
                         TRUE ~ .x
                       ))) |>
  dplyr::mutate(iraq_coalition_general = case_when(
    ccode %in% iraq.ccode.list ~ 1,
    TRUE ~ 0
  )) |> 
  dplyr::filter(ccode != 70) |> 
  dplyr::select(!contains("country."), !contains("region.")) |>
  dplyr::mutate(row_index = row_number())



# Generate limited nested dataset for comparison
# Complete cases on exactly the variables entering the five models:
#   Economic:  gdppc_z, imports_from_us_z, population_total_z, population_urban_z
#   Political: v2x_polyarchy_z, un_distance_z, alba_member, iraq_coalition
#   Need:      infant_mortality_rate_z, homicide_rate_z, education_spending_z, healthcare_expenditures_z
#   Full adds: s(year) + (1|countryname) + gp(capital.lat, capital.lon)
data.analysis.nested <- data.analysis |> 
  drop_na(deployment_lead_1, deployment_lead_2,
          gdppc_z, imports_from_us_z, population_total_z, population_urban_z,
          v2x_polyarchy_z, un_distance_z, alba_member, iraq_coalition,
          infant_mortality_rate_z, homicide_rate_z, education_spending_z, healthcare_expenditures_z,
          capital.lat, capital.lon) |> 
  dplyr::mutate(row_index = row_number())
  

# Write data file for main data
readr::write_csv(data.analysis,
                 here::here("Data/data-analysis.csv"))


# Write data file for nested data
readr::write_csv(data.analysis.nested,
                 here::here("Data/data-analysis-nested.csv"))



```





# Analysis

## Create Map of Deployment Locations

```{r deployment-map}

deploy.count <- data.analysis |>
  dplyr::select(countryname, year, deployment) |> 
  filter(year >= 1998) |> 
  dplyr::rename("Country" = "countryname", "Year" = "year") |> 
  group_by(Country) |>
  dplyr::summarise(Count = sum(deployment, na.rm = TRUE)) 


mapdata <- rnaturalearth::ne_countries(scale = "medium", returnclass = "sf") |> 
  dplyr::filter(region_wb == "Latin America & Caribbean") |> 
  dplyr::left_join(deploy.count, by = c("name" = "Country")) |>
  dplyr::mutate(Count = ifelse(is.na(Count), 0, Count)) |> 
  dplyr::filter(sovereignt != "Mexico")

coastline <- rnaturalearth::ne_coastline(scale = "medium",
                                         returnclass = "sf")

mapplot <- ggplot() +
  geom_sf(data = coastline,
          aes(geometry = geometry),
          linewidth = 0.1) +
  geom_sf(data = mapdata, 
          aes(fill = Count),
          color = "black", size = 0.1) +

  viridis::scale_fill_viridis(option = "turbo",
                              begin = 0.05,
                              end = 1.0,
                              direction = 1) +
  flynnprojects::theme_flynn_map(base_size = 11, base_family = "oswald") +
  theme(plot.title = element_text(size = rel(1.2))) +
  guides(fill = "none") +
  coord_sf(xlim = c(-100, -30),
           ylim = c(25.25, -57.3)) +
  theme(legend.title = element_text(margin = margin(b = 8))) +
  labs(title = "Humanitarian and Civic Assistance Deployment Locations, 1998-2025",
       fill = "Number of\nDeployments") 

ggsave(here::here("Figures/deployment_map.png"), 
       width = 6, 
       height = 4, 
       dpi = 400)

# Generate histogram with coloring.

histplot <- ggplot(deploy.count, aes(x = Count, group = Count, fill = Count)) +
  geom_histogram(binwidth = 1,
                 show.legend = FALSE,
                 linewidth = 0.1,
                 color = "black") +
  viridis::scale_fill_viridis(option = "turbo",
                              begin = 0.05,
                              end = 1.0,
                              direction = 1) +
  flynnprojects::theme_flynn_map(base_size = 6, base_family = "oswald") + 
  theme(axis.text.x.bottom = element_text(),
        axis.title.x.bottom = element_text(size = rel(1.1),
                                           margin = margin(t = 0.2, unit = "cm"))) +
  scale_x_continuous(breaks = seq(0,17,1)) +
  labs(x = "Count",
       y  = "",
       fill = "Count")


## Create table for top five recipients

tableplot <- gt::gt(deploy.count |> 
                                     arrange(-Count) |> 
                                     slice(1:5)) |> 
  gt::tab_header(title = "Top 5 Deployment Locations") |> 
  gt::tab_options(table.font.size = 9,
                  heading.title.font.weight = "bold",
                  column_labels.font.weight = "bold")
  
  
  
## Combine all into single plot
com.1 <- mapplot + 
  inset_element(histplot,
                left = 0.79,
                right = 1.43,
                bottom = 0.20,
                top = 0.48,
                align_to = "full",
                on_top = FALSE) 

com.2 <- com.1 + 
  inset_element(tableplot,
                left = 0.92,
                right = 0.90,
                bottom = 0.60,
                top = 0.80,
                align_to = "full",
                on_top = FALSE) 

ggsave(here::here("Figures/deployment_map_full.png"), 
       width = 9,
       height = 5, 
       dpi = 400)


```




## Model Settings
 
```{r model-settings}
#| echo: false
#| message: false
 
# ---- Sampler settings: shared by EVERY model in EVERY block ----------------
ITERS     <- 7000
CHAINS    <- 4
WARMUP    <- ITERS / 2
CORES     <- 4
THIN      <- 1
SEED      <- 66502
ADAPT     <- 0.99
TREEDEPTH <- 13
THREADS   <- 2
 
# ---- Priors ---------------------------------------------------------------
# Fixed-effects-only models (Economic, Political, Need, Combined)
# Fixed-effects-only models (Economic, Political, Need, Combined)
PRIORS.INTERCEPT <- c(
  prior(normal(0, 1),   class = "Intercept"),
  prior(gamma(1, 1), class = "sd",  coef  = "Intercept", group = "countryname"),
  prior(gamma(1, 1), class = "sd",  group = "countryname")
)

PRIORS.FIXED <- c(
  prior(normal(0, 0.5), class = "b"),
  prior(normal(0, 1),   class = "Intercept"),
  prior(gamma(1, 1), class = "sd",  coef  = "Intercept", group = "countryname"),
  prior(gamma(1, 1), class = "sd",  group = "countryname")
)
 
# Full models (varying intercepts + year smooth + spatial GP)
PRIORS.FULL <- c(
  prior(normal(0, 0.5), class = "b"),
  prior(normal(0, 1),   class = "Intercept"),
  prior(gamma(1, 1), class = "sd",  group = "countryname"),
  prior(gamma(1, 1), class = "sd",  coef  = "Intercept", group = "countryname"),
  prior(gamma(1, 1), class = "sds", coef  = "s(year)"),
  prior(gamma(1, 1),     class = "sdgp"),
  prior(inv_gamma(4, 1), class = "lscale")
)
```
 
 
 
## Models
 
### Full Models
 
```{r brms-models-base-lead-1}
#| echo: false
#| message: false
 
model.intercepts.l1 <- brm(
  deployment_lead_1 ~ (1|countryname),
  data       = data.analysis,
  prior      = PRIORS.INTERCEPT,
  family     = bernoulli(link = "logit"),
  chains     = CHAINS,
  iter       = ITERS,
  warmup     = WARMUP,
  cores      = CORES,
  thin       = THIN,
  seed       = SEED,
  backend    = "cmdstanr",
  threads    = threading(THREADS),
  control    = list(adapt_delta = ADAPT, max_treedepth = TREEDEPTH),
  file       = here::here("Models/intercept_model_lead_1.rds"),
  file_refit = "on_change"
)

model.econ.l1 <- brm(
  deployment_lead_1 ~ gdppc_z + imports_from_us_z + population_total_z + population_urban_z + (1|countryname),
  data       = data.analysis,
  prior      = PRIORS.FIXED,
  family     = bernoulli(link = "logit"),
  chains     = CHAINS,
  iter       = ITERS,
  warmup     = WARMUP,
  cores      = CORES,
  thin       = THIN,
  seed       = SEED,
  backend    = "cmdstanr",
  threads    = threading(THREADS),
  control    = list(adapt_delta = ADAPT, max_treedepth = TREEDEPTH),
  file       = here::here("Models/econ_model_lead_1.rds"),
  file_refit = "on_change"
)
 
model.political.l1 <- brm(
  deployment_lead_1 ~ v2x_polyarchy_z + un_distance_z + executive_alignment + asylum_refugee_total_z + (1|countryname),
  data       = data.analysis,
  prior      = PRIORS.FIXED,
  family     = bernoulli(link = "logit"),
  chains     = CHAINS,
  iter       = ITERS,
  warmup     = WARMUP,
  cores      = CORES,
  thin       = THIN,
  seed       = SEED,
  backend    = "cmdstanr",
  threads    = threading(THREADS),
  control    = list(adapt_delta = ADAPT, max_treedepth = TREEDEPTH),
  file       = here::here("Models/political_model_lead_1.rds"),
  file_refit = "on_change"
)
 

model.need.l1 <- brm(
  deployment_lead_1 ~ infant_mortality_rate_z + homicide_rate_z + education_spending_z + healthcare_expenditures_z + (1|countryname),
  data       = data.analysis,
  prior      = PRIORS.FIXED,
  family     = bernoulli(link = "logit"),
  chains     = CHAINS,
  iter       = ITERS,
  warmup     = WARMUP,
  cores      = CORES,
  thin       = THIN,
  seed       = SEED,
  backend    = "cmdstanr",
  threads    = threading(THREADS),
  control    = list(adapt_delta = ADAPT, max_treedepth = TREEDEPTH),
  file       = here::here("Models/need_model_lead_1.rds"),
  file_refit = "on_change"
)
 

model.combined.l1 <- brm(
  deployment_lead_1 ~ gdppc_z + imports_from_us_z + population_total_z + population_urban_z +
    v2x_polyarchy_z + un_distance_z + executive_alignment + refugee_asylum_total_z +
    infant_mortality_rate_z + homicide_rate_z + education_spending_z + healthcare_expenditures_z  + (1|countryname),
  data       = data.analysis.nested,
  prior      = PRIORS.FIXED,
  family     = bernoulli(link = "logit"),
  chains     = CHAINS,
  iter       = ITERS,
  warmup     = WARMUP,
  cores      = CORES,
  thin       = THIN,
  seed       = SEED,
  backend    = "cmdstanr",
  threads    = threading(THREADS),
  control    = list(adapt_delta = ADAPT, max_treedepth = TREEDEPTH),
  file       = here::here("Models/combined_model_lead_1.rds"),
  file_refit = "on_change"
)


model.full.l1 <- brm(
  deployment_lead_1 ~ gdppc_z + imports_from_us_z + population_total_z + population_urban_z +
    v2x_polyarchy_z + un_distance_z + executive_alignment + refugee_asylum_total_z +
    infant_mortality_rate_z + homicide_rate_z + education_spending_z + healthcare_expenditures_z +
    s(year) + (1 | countryname) + gp(capital.lat, capital.lon),
  data       = data.analysis,
  prior      = PRIORS.FULL,
  family     = bernoulli(link = "logit"),
  chains     = CHAINS,
  iter       = ITERS,
  warmup     = WARMUP,
  cores      = CORES,
  thin       = THIN,
  seed       = SEED,
  backend    = "cmdstanr",
  threads    = threading(THREADS),
  control    = list(adapt_delta = ADAPT, max_treedepth = TREEDEPTH),
  file       = here::here("Models/full_model_lead_1.rds"),
  file_refit = "on_change"
)
```
 
```{r brms-models-base-lead-2}
#| echo: false
#| message: false
 
model.intercepts.l2 <- brm(
  deployment_lead_2 ~ (1|countryname),
  data       = data.analysis,
  prior      = PRIORS.INTERCEPT,
  family     = bernoulli(link = "logit"),
  chains     = CHAINS,
  iter       = ITERS,
  warmup     = WARMUP,
  cores      = CORES,
  thin       = THIN,
  seed       = SEED,
  backend    = "cmdstanr",
  threads    = threading(THREADS),
  control    = list(adapt_delta = ADAPT, max_treedepth = TREEDEPTH),
  file       = here::here("Models/intercept_model_lead_2.rds"),
  file_refit = "on_change"
)

model.econ.l2 <- brm(
  deployment_lead_2 ~ gdppc_z + imports_from_us_z + population_total_z + population_urban_z + (1|countryname),
  data       = data.analysis,
  prior      = PRIORS.FIXED,
  family     = bernoulli(link = "logit"),
  chains     = CHAINS,
  iter       = ITERS,
  warmup     = WARMUP,
  cores      = CORES,
  thin       = THIN,
  seed       = SEED,
  backend    = "cmdstanr",
  threads    = threading(THREADS),
  control    = list(adapt_delta = ADAPT, max_treedepth = TREEDEPTH),
  file       = here::here("Models/econ_model_lead_2.rds"),
  file_refit = "on_change"
)
 
model.political.l2 <- brm(
  deployment_lead_2 ~ v2x_polyarchy_z + un_distance_z + executive_alignment + asylum_refugee_total_z + (1|countryname),
  data       = data.analysis,
  prior      = PRIORS.FIXED,
  family     = bernoulli(link = "logit"),
  chains     = CHAINS,
  iter       = ITERS,
  warmup     = WARMUP,
  cores      = CORES,
  thin       = THIN,
  seed       = SEED,
  backend    = "cmdstanr",
  threads    = threading(THREADS),
  control    = list(adapt_delta = ADAPT, max_treedepth = TREEDEPTH),
  file       = here::here("Models/political_model_lead_2.rds"),
  file_refit = "on_change"
)
 
model.need.l2 <- brm(
  deployment_lead_2 ~ infant_mortality_rate_z + homicide_rate_z + education_spending_z + healthcare_expenditures_z + (1|countryname),
  data       = data.analysis,
  prior      = PRIORS.FIXED,
  family     = bernoulli(link = "logit"),
  chains     = CHAINS,
  iter       = ITERS,
  warmup     = WARMUP,
  cores      = CORES,
  thin       = THIN,
  seed       = SEED,
  backend    = "cmdstanr",
  threads    = threading(THREADS),
  control    = list(adapt_delta = ADAPT, max_treedepth = TREEDEPTH),
  file       = here::here("Models/need_model_lead_2.rds"),
  file_refit = "on_change"
)
 

model.combined.l2 <- brm(
  deployment_lead_2 ~ gdppc_z + imports_from_us_z + population_total_z + population_urban_z +
    v2x_polyarchy_z + un_distance_z + executive_alignment + refugee_asylum_total_z +
    infant_mortality_rate_z + homicide_rate_z + education_spending_z + healthcare_expenditures_z  + (1|countryname),
  data       = data.analysis.nested,
  prior      = PRIORS.FIXED,
  family     = bernoulli(link = "logit"),
  chains     = CHAINS,
  iter       = ITERS,
  warmup     = WARMUP,
  cores      = CORES,
  thin       = THIN,
  seed       = SEED,
  backend    = "cmdstanr",
  threads    = threading(THREADS),
  control    = list(adapt_delta = ADAPT, max_treedepth = TREEDEPTH),
  file       = here::here("Models/combined_model_nested_lead_2.rds"),
  file_refit = "on_change"
)


 
model.full.l2 <- brm(
  deployment_lead_2 ~ gdppc_z + imports_from_us_z + population_total_z + population_urban_z +
    v2x_polyarchy_z + un_distance_z + executive_alignment + refugee_asylum_total_z +
    infant_mortality_rate_z + homicide_rate_z + education_spending_z + healthcare_expenditures_z +
    s(year) + (1 | countryname) + gp(capital.lat, capital.lon),
  data       = data.analysis,
  prior      = PRIORS.FULL,
  family     = bernoulli(link = "logit"),
  chains     = CHAINS,
  iter       = ITERS,
  warmup     = WARMUP,
  cores      = CORES,
  thin       = THIN,
  seed       = SEED,
  backend    = "cmdstanr",
  threads    = threading(THREADS),
  control    = list(adapt_delta = ADAPT, max_treedepth = TREEDEPTH),
  file       = here::here("Models/full_model_lead_2.rds"),
  file_refit = "on_change"
)
```
 
### Nested Models
 
```{r brms-models-nested-lead-1}
#| echo: false
#| message: false
 
model.intercepts.nested.l1 <- brm(
  deployment_lead_1 ~ (1|countryname),
  data       = data.analysis.nested,
  prior      = PRIORS.INTERCEPT,
  family     = bernoulli(link = "logit"),
  chains     = CHAINS,
  iter       = ITERS,
  warmup     = WARMUP,
  cores      = CORES,
  thin       = THIN,
  seed       = SEED,
  backend    = "cmdstanr",
  threads    = threading(THREADS),
  control    = list(adapt_delta = ADAPT, max_treedepth = TREEDEPTH),
  file       = here::here("Models/intercept_model_nested_lead_1.rds"),
  file_refit = "on_change"
)

model.econ.nested.l1 <- brm(
  deployment_lead_1 ~ gdppc_z + imports_from_us_z + population_total_z + population_urban_z  + (1|countryname),
  data       = data.analysis.nested,
  prior      = PRIORS.FIXED,
  family     = bernoulli(link = "logit"),
  chains     = CHAINS,
  iter       = ITERS,
  warmup     = WARMUP,
  cores      = CORES,
  thin       = THIN,
  seed       = SEED,
  backend    = "cmdstanr",
  threads    = threading(THREADS),
  control    = list(adapt_delta = ADAPT, max_treedepth = TREEDEPTH),
  file       = here::here("Models/econ_model_nested_lead_1.rds"),
  file_refit = "on_change"
)
 
model.political.nested.l1 <- brm(
  deployment_lead_1 ~ v2x_polyarchy_z + un_distance_z + executive_alignment + refugee_asylum_total_z  + (1|countryname),
  data       = data.analysis.nested,
  prior      = PRIORS.FIXED,
  family     = bernoulli(link = "logit"),
  chains     = CHAINS,
  iter       = ITERS,
  warmup     = WARMUP,
  cores      = CORES,
  thin       = THIN,
  seed       = SEED,
  backend    = "cmdstanr",
  threads    = threading(THREADS),
  control    = list(adapt_delta = ADAPT, max_treedepth = TREEDEPTH),
  file       = here::here("Models/political_model_nested_lead_1.rds"),
  file_refit = "on_change"
)
 
model.need.nested.l1 <- brm(
  deployment_lead_1 ~ infant_mortality_rate_z + homicide_rate_z + education_spending_z + healthcare_expenditures_z  + (1|countryname),
  data       = data.analysis.nested,
  prior      = PRIORS.FIXED,
  family     = bernoulli(link = "logit"),
  chains     = CHAINS,
  iter       = ITERS,
  warmup     = WARMUP,
  cores      = CORES,
  thin       = THIN,
  seed       = SEED,
  backend    = "cmdstanr",
  threads    = threading(THREADS),
  control    = list(adapt_delta = ADAPT, max_treedepth = TREEDEPTH),
  file       = here::here("Models/need_model_nested_lead_1.rds"),
  file_refit = "on_change"
)
 

model.combined.nested.l1 <- brm(
  deployment_lead_1 ~ gdppc_z + imports_from_us_z + population_total_z + population_urban_z +
    v2x_polyarchy_z + un_distance_z + executive_alignment + refugee_asylum_total_z +
    infant_mortality_rate_z + homicide_rate_z + education_spending_z + healthcare_expenditures_z  + (1|countryname),
  data       = data.analysis.nested,
  prior      = PRIORS.FIXED,
  family     = bernoulli(link = "logit"),
  chains     = CHAINS,
  iter       = ITERS,
  warmup     = WARMUP,
  cores      = CORES,
  thin       = THIN,
  seed       = SEED,
  backend    = "cmdstanr",
  threads    = threading(THREADS),
  control    = list(adapt_delta = ADAPT, max_treedepth = TREEDEPTH),
  file       = here::here("Models/combined_model_nested_lead_1.rds"),
  file_refit = "on_change"
)

model.full.nested.l1 <- brm(
  deployment_lead_1 ~ gdppc_z + imports_from_us_z + population_total_z + population_urban_z +
    v2x_polyarchy_z + un_distance_z + executive_alignment + refugee_asylum_total_z +
    infant_mortality_rate_z + homicide_rate_z + education_spending_z + healthcare_expenditures_z +
    s(year) + (1 | countryname) + gp(capital.lat, capital.lon),
  data       = data.analysis.nested,
  prior      = PRIORS.FULL,
  family     = bernoulli(link = "logit"),
  chains     = CHAINS,
  iter       = ITERS,
  warmup     = WARMUP,
  cores      = CORES,
  thin       = THIN,
  seed       = SEED,
  backend    = "cmdstanr",
  threads    = threading(THREADS),
  control    = list(adapt_delta = ADAPT, max_treedepth = TREEDEPTH),
  file       = here::here("Models/full_model_nested_lead_1.rds"),
  file_refit = "on_change"
)
```
 
```{r brms-models-nested-lead-2}
#| echo: false
#| message: false
 
model.intercepts.nested.l2 <- brm(
  deployment_lead_2 ~ (1|countryname),
  data       = data.analysis.nested,
  prior      = PRIORS.INTERCEPT,
  family     = bernoulli(link = "logit"),
  chains     = CHAINS,
  iter       = ITERS,
  warmup     = WARMUP,
  cores      = CORES,
  thin       = THIN,
  seed       = SEED,
  backend    = "cmdstanr",
  threads    = threading(THREADS),
  control    = list(adapt_delta = ADAPT, max_treedepth = TREEDEPTH),
  file       = here::here("Models/intercept_model_nested_lead_2.rds"),
  file_refit = "on_change"
)

model.econ.nested.l2 <- brm(
  deployment_lead_2 ~ gdppc_z + imports_from_us_z + population_total_z + population_urban_z  + (1|countryname),
  data       = data.analysis.nested,
  prior      = PRIORS.FIXED,
  family     = bernoulli(link = "logit"),
  chains     = CHAINS,
  iter       = ITERS,
  warmup     = WARMUP,
  cores      = CORES,
  thin       = THIN,
  seed       = SEED,
  backend    = "cmdstanr",
  threads    = threading(THREADS),
  control    = list(adapt_delta = ADAPT, max_treedepth = TREEDEPTH),
  file       = here::here("Models/econ_model_nested_lead_2.rds"),
  file_refit = "on_change"
)
 
model.political.nested.l2 <- brm(
  deployment_lead_2 ~ v2x_polyarchy_z + un_distance_z + executive_alignment + refugee_asylum_total_z  + (1|countryname),
  data       = data.analysis.nested,
  prior      = PRIORS.FIXED,
  family     = bernoulli(link = "logit"),
  chains     = CHAINS,
  iter       = ITERS,
  warmup     = WARMUP,
  cores      = CORES,
  thin       = THIN,
  seed       = SEED,
  backend    = "cmdstanr",
  threads    = threading(THREADS),
  control    = list(adapt_delta = ADAPT, max_treedepth = TREEDEPTH),
  file       = here::here("Models/political_model_nested_lead_2.rds"),
  file_refit = "on_change"
)
 
model.need.nested.l2 <- brm(
  deployment_lead_2 ~ infant_mortality_rate_z + homicide_rate_z + education_spending_z + healthcare_expenditures_z  + (1|countryname),
  data       = data.analysis.nested,
  prior      = PRIORS.FIXED,
  family     = bernoulli(link = "logit"),
  chains     = CHAINS,
  iter       = ITERS,
  warmup     = WARMUP,
  cores      = CORES,
  thin       = THIN,
  seed       = SEED,
  backend    = "cmdstanr",
  threads    = threading(THREADS),
  control    = list(adapt_delta = ADAPT, max_treedepth = TREEDEPTH),
  file       = here::here("Models/need_model_nested_lead_2.rds"),
  file_refit = "on_change"
)
 
model.combined.nested.l2 <- brm(
  deployment_lead_2 ~ gdppc_z + imports_from_us_z + population_total_z + population_urban_z +
    v2x_polyarchy_z + un_distance_z + executive_alignment + refugee_asylum_total_z +
    infant_mortality_rate_z + homicide_rate_z + education_spending_z + healthcare_expenditures_z  + (1|countryname),
  data       = data.analysis.nested,
  prior      = PRIORS.FIXED,
  family     = bernoulli(link = "logit"),
  chains     = CHAINS,
  iter       = ITERS,
  warmup     = WARMUP,
  cores      = CORES,
  thin       = THIN,
  seed       = SEED,
  backend    = "cmdstanr",
  threads    = threading(THREADS),
  control    = list(adapt_delta = ADAPT, max_treedepth = TREEDEPTH),
  file       = here::here("Models/combined_model_nested_lead_2.rds"),
  file_refit = "on_change"
)
 
model.full.nested.l2 <- brm(
  deployment_lead_2 ~ gdppc_z + imports_from_us_z + population_total_z + population_urban_z +
    v2x_polyarchy_z + un_distance_z + executive_alignment + refugee_asylum_total_z +
    infant_mortality_rate_z + homicide_rate_z + education_spending_z + healthcare_expenditures_z +
    s(year) + (1 | countryname) + gp(capital.lat, capital.lon),
  data       = data.analysis.nested,
  prior      = PRIORS.FULL,
  family     = bernoulli(link = "logit"),
  chains     = CHAINS,
  iter       = ITERS,
  warmup     = WARMUP,
  cores      = CORES,
  thin       = THIN,
  seed       = SEED,
  backend    = "cmdstanr",
  threads    = threading(THREADS),
  control    = list(adapt_delta = ADAPT, max_treedepth = TREEDEPTH),
  file       = here::here("Models/full_model_nested_lead_2.rds"),
  file_refit = "on_change"
)
```




## Tables


### Full Model 

```{r tables-full-model}
#| echo: false
#| message: false

# Set model list
mod.list <- list("Intercepts" = model.intercepts.l1,
                 "Economic" = model.econ.l1,
                 "Political" = model.political.l1,
                 "Need" = model.need.l1,
                 "Combined" = model.combined.l1,
                 "Full" = model.full.l1)

# Set coefficient names 
coef.names <- c("b_Intercept" = "Intercept",
                "b_gdppc_z" = "GDP Per Capita",
                "b_imports_from_us_z" = "Imports from US",
                "b_population_total_z" = "Total Population",
                "b_population_urban_z" = "Percent Urban Population",
                "b_v2x_polyarchy_z" = "Polyarchy Score",
                "b_un_distance_z" = "UN Voting Distance",
                "b_executive_alignment" = "Executive Alignment",
                "b_refugee_asylum_total_z" = "Total Asylum and Refugee Grants",
                "b_infant_mortality_rate_z" = "Infant Mortality Rate",
                "b_homicide_rate_z" = "Homicide Rate",
                "b_healthcare_expenditures_z" = "Healthcare Expenditures",
                "b_education_spending_z" = "Education Spending")


# Set goodness of fit statistics
gof.names <- c("nobs",
               "ngroups",
               "nclusters",
               "elpd",
               "waic",
               "looic"
               )

# Set group index
group.index <- as.data.frame(coef.names) |> 
  dplyr::mutate(group = c("Intercept",
                          "Economic", "Economic", "Economic", "Economic",
                          "Political", "Political", "Political", "Political",
                          "Need", "Need", "Need", "Need")
                ) |> 
  rownames_to_column(var = "raw") |> 
  dplyr::rename("clean" = "coef.names") 


stat.list <- tibble::tribble(~term, ~term, ~term, ~term, ~term, ~term, ~term,
  "Varying Intercepts", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
  "Group Num.", glue::glue("{n_distinct(mod.list[[1]]$data$countryname)}"),
  glue::glue("{n_distinct(mod.list[[2]]$data$countryname)}"),
  glue::glue("{n_distinct(mod.list[[3]]$data$countryname)}"),
  glue::glue("{n_distinct(mod.list[[4]]$data$countryname)}"),
  glue::glue("{n_distinct(mod.list[[5]]$data$countryname)}"), glue::glue("{n_distinct(mod.list[[6]]$data$countryname)}"),
  "Temporal Spline", "No", "No", "No", "No", "No", "Yes",
  "Spatial GP", "No", "No", "No", "No", "No", "Yes"
)



tab <- modelsummary(mod.list,
             estimate = "{estimate} [{conf.low}, {conf.high}]",
             coef_map = coef.names,
             gof_map = gof.names,
             fmt = 2,
             booktabs = TRUE,
             add_rows = stat.list,
             title = "Bayesian logistic models predicting deployments \\label{tab:cymodels}") 


tab.formatted <- tab |> 
  tinytable::group_tt(i = list(
    "Intercept" = 1,
    "Economic" = 2,
    "Political" = 6,
    "Need" = 10,
    "Model Fit" = 14
  )) |> 
  tinytable::style_tt(fontsize = 0.9) |> 
  tinytable::group_tt(j = list("(1)" = 2, "(2)" = 3, "(3)" = 4, "(4)" = 5, "(5)" = 6, "(6)" = 7)) |> 
  tinytable::style_tt(i = c(1,3,8,13,18),
                      background = "gray",
                      bold = TRUE) |>
  tinytable::style_tt(i = 14,
                      line = "b",
                      line_width = 0.1,
                      line_color = "white") |>
  tinytable::style_tt(i = 17,
                      line = "b",
                      line_width = 0.2,
                      line_color = "black") |> 
  theme_latex(resize_height = 0.5,
              resize_width = 0.2,
              resize_direction = "both") |> 
  #theme_rotate() |> 
  tinytable::save_tt(here::here("Tables/model_summary_base.tex"),
                     overwrite = TRUE)


```


### Nested Models

```{r tables-nested-models}
#| echo: false
#| message: false

# Set model list
mod.list <- list("Intercepts" = model.intercepts.nested.l1,
                 "Economic" = model.econ.nested.l1,
                 "Political" = model.political.nested.l1,
                 "Need" = model.need.nested.l1,
                 "Combined" = model.combined.nested.l1,
                 "Full" = model.full.nested.l1)

# Set coefficient names 
coef.names <- c("b_Intercept" = "Intercept",
                "b_gdppc_z" = "GDP Per Capita",
                "b_imports_from_us_z" = "Imports from US",
                "b_population_total_z" = "Total Population",
                "b_population_urban_z" = "Percent Urban Population",
                "b_v2x_polyarchy_z" = "Polyarchy Score",
                "b_un_distance_z" = "UN Voting Distance",
                "b_executive_alignment" = "Executive Alignment",
                "b_refugee_asylum_total_z" = "Total Asylum and Refugee Grants",
                "b_infant_mortality_rate_z" = "Infant Mortality Rate",
                "b_homicide_rate_z" = "Homicide Rate",
                "b_healthcare_expenditures_z" = "Healthcare Expenditures",
                "b_education_spending_z" = "Education Spending")


# Set goodness of fit statistics
gof.names <- c("nobs",
               "ngroups",
               "nclusters",
               "elpd",
               "waic",
               "looic"
               )

# Set group index
group.index <- as.data.frame(coef.names) |> 
  dplyr::mutate(group = c("Intercept",
                          "Economic", "Economic", "Economic", "Economic",
                          "Political", "Political", "Political", "Political",
                          "Need", "Need", "Need", "Need")
                ) |> 
  rownames_to_column(var = "raw") |> 
  dplyr::rename("clean" = "coef.names") 




stat.list <- tibble::tribble(~term, ~term, ~term, ~term, ~term, ~term, ~term,
  "Varying Intercepts", "Yes", "Yes", "Yes", "Yes", "Yes", "Yes",
  "Group Num.", glue::glue("{n_distinct(mod.list[[1]]$data$countryname)}"),
  glue::glue("{n_distinct(mod.list[[2]]$data$countryname)}"),
  glue::glue("{n_distinct(mod.list[[3]]$data$countryname)}"),
  glue::glue("{n_distinct(mod.list[[4]]$data$countryname)}"),
  glue::glue("{n_distinct(mod.list[[5]]$data$countryname)}"), glue::glue("{n_distinct(mod.list[[6]]$data$countryname)}"),
  "Temporal Spline", "No", "No", "No", "No", "No", "Yes",
  "Spatial GP", "No", "No", "No", "No", "No", "Yes"
)



tab <- modelsummary(mod.list,
             estimate = "{estimate} [{conf.low}, {conf.high}]",
             coef_map = coef.names,
             gof_map = gof.names,
             fmt = 2,
             booktabs = TRUE,
             add_rows = stat.list,
             #width = 1.3,
             title = "Bayesian logistic models predicting deployments (Nested) \\label{tab:cymodelsnested}") 


tab.formatted <- tab |> 
  tinytable::group_tt(i = list(
    "Intercept" = 1,
    "Economic" = 2,
    "Political" = 6,
    "Need" = 10,
    "Model Fit" = 14
  )) |> 
  tinytable::style_tt(fontsize = 0.9) |> 
    tinytable::group_tt(j = list("(1)" = 2, "(2)" = 3, "(3)" = 4, "(4)" = 5, "(5)" = 6, "(6)" = 7)) |> 

  tinytable::style_tt(i = c(1,3,8,13,18),
                      background = "gray",
                      bold = TRUE) |>
  tinytable::style_tt(i = 14,
                      line = "b",
                      line_width = 0.1,
                      line_color = "white") |>
  tinytable::style_tt(i = 17,
                      line = "b",
                      line_width = 0.2,
                      line_color = "black") |> 
  theme_latex(resize_height = 0.5,
              resize_width = 0.2,
              resize_direction = "both") |>
  #theme_rotate() |> 
  tinytable::save_tt(here::here("Tables/model_summary_nested.tex"),
                     overwrite = TRUE)
```



# Figures



### Coefficient Plots

```{r coefficient-plots-base}


# Coefficient plots for the base models

set.seed(66502)

mod.list <- list(model.econ.l1,
                 model.political.l1,
                 model.need.l1,
                 model.combined.l1,
                 model.full.l1)

mod.names <- c("Economic", "Political", "Need", "Combined", "Full")

names(mod.list) <- mod.names

coef.plot <- purrr::map2(.x = seq_along(mod.list),
                         .y = seq_along(mod.names),
                        .f = ~brms::as_draws_df(mod.list[[.x]],
                                             variable = "b_",
                                             regex = TRUE) |> 
                          dplyr::slice_sample(n = 200) |> 
                          dplyr::select(-b_Intercept) |> 
                          tidyr::pivot_longer(cols = everything()) |> 
                          dplyr::mutate(`Model Group` = mod.names[[.y]],
                                        name.full = case_when(
                                          grepl(".*poly.*", name) ~ "Polyarchy Score",
                                          grepl(".*dist.*", name) ~ "UN Distance",
                                          grepl(".*asyl*", name) ~ "Total Asylum and Refugee Grants",
                                          grepl(".*exec.*", name) ~ "Executive Alignment",
                                          grepl(".*infant.*", name) ~ "Infant Mortality Rate",
                                          grepl(".*homicide.*", name) ~ "Homicide Rate",
                                          grepl(".*educ.*", name) ~ "Education Spending",
                                          grepl(".*health.*", name) ~ "Healthcare Spending",
                                          grepl(".*import.*", name) ~ "Imports from US",
                                          grepl(".*_total.*", name) ~ "Population (Total)",
                                          grepl(".*_urban.*", name) ~ "Population (Urban)",
                                          grepl(".*gdppc.*", name) ~ "GDP Per Capita"
                                        )
                                        )
                        )

coef.plot.df.base <- data.table::rbindlist(coef.plot) |> 
  dplyr::filter(!is.na(name.full)) |> 
  dplyr::mutate(name.full = factor(name.full,
                                   levels = c("GDP Per Capita", "Imports from US", "Population (Total)", "Population (Urban)",
                                              "Polyarchy Score", "UN Distance", "Total Asylum and Refugee Grants", "Executive Alignment",
                                              "Infant Mortality Rate", "Education Spending", "Healthcare Spending", "Homicide Rate"))) |> 
  dplyr::mutate(`Model Group` = factor(`Model Group`,
                                       levels = c("Full", "Combined", "Need", "Political", "Economic")))


coef.plot.base <- ggplot(coef.plot.df.base, aes(y = reorder(name.full, -as.numeric(name.full)), x = value, color = `Model Group`, fill = `Model Group`)) +
  ggdist::stat_slabinterval(.width = c(0.5, 0.89),
                            position = "dodge",
                            color = "black",
                            slab_alpha = 0.5) +
  geom_vline(xintercept = 0) +
  facet_grid(name.full ~ .,
             scales = "free",
             switch="both") +
  viridis::scale_fill_viridis(option = "magma",
                              discrete = TRUE,
                              begin = 0.2,
                              end = 0.9) +
  guides(color = guide_legend(reverse = TRUE),
         fill = guide_legend(reverse = TRUE)) +
  theme_flynn(base_size = 11, base_family = "oswald") +
  theme(strip.text.y.left = element_text(size = 8, angle = 0, hjust = 0),
        axis.text.y = element_blank(),
        axis.ticks.y.left = element_blank()) +
  labs(x = "Estimate",
       y = "Coefficient",
       title = "Base")

coef.plot.base

ggsave(here::here("Figures/coefficient-plot.png"),
       width = 7.5,
       height = 8.5,
       unit = "in")




```




```{r coefficient-plots-nested}


# Coefficient plots for the base models

set.seed(66502)

mod.list <- list(model.econ.nested.l1,
                 model.political.nested.l1,
                 model.need.nested.l1,
                 model.combined.nested.l1,
                 model.full.nested.l1)

mod.names <- c("Economic", "Political", "Need", "Combined", "Full")

names(mod.list) <- mod.names

coef.plot.df <- purrr::map2(.x = seq_along(mod.list),
                         .y = seq_along(mod.names),
                        .f = ~brms::as_draws_df(mod.list[[.x]],
                                             variable = "b_",
                                             regex = TRUE) |> 
                          dplyr::slice_sample(n = 200) |> 
                          dplyr::select(-b_Intercept) |> 
                          tidyr::pivot_longer(cols = everything()) |> 
                          dplyr::mutate(`Model Group` = mod.names[[.y]],
                                        name.full = case_when(
                                          grepl(".*poly.*", name) ~ "Polyarchy Score",
                                          grepl(".*dist.*", name) ~ "UN Distance",
                                          grepl(".*asyl*", name) ~ "Total Asylum and Refugee Grants",
                                          grepl(".*exec.*", name) ~ "Executive Alignment",
                                          grepl(".*infant.*", name) ~ "Infant Mortality Rate",
                                          grepl(".*homicide.*", name) ~ "Homicide Rate",
                                          grepl(".*educ.*", name) ~ "Education Spending",
                                          grepl(".*health.*", name) ~ "Healthcare Spending",
                                          grepl(".*import.*", name) ~ "Imports from US",
                                          grepl(".*_total.*", name) ~ "Population (Total)",
                                          grepl(".*_urban.*", name) ~ "Population (Urban)",
                                          grepl(".*gdppc.*", name) ~ "GDP Per Capita"
                                        )
                                        )
                        )

coef.plot.df.nested <- data.table::rbindlist(coef.plot.df) |> 
  dplyr::filter(!is.na(name.full)) |> 
  dplyr::mutate(name.full = factor(name.full,
                                   levels = c("GDP Per Capita", "Imports from US", "Population (Total)", "Population (Urban)",
                                              "Polyarchy Score", "UN Distance", "Total Asylum and Refugee Grants", "Executive Alignment",
                                              "Infant Mortality Rate", "Education Spending", "Healthcare Spending", "Homicide Rate"))) |> 
  dplyr::mutate(`Model Group` = factor(`Model Group`,
                                       levels = c("Full", "Combined", "Need", "Political", "Economic")))


coef.plot.nested <- ggplot(coef.plot.df.nested, aes(y = reorder(name.full, -as.numeric(name.full)), x = value, color = `Model Group`, fill = `Model Group`)) +
  ggdist::stat_slabinterval(.width = c(0.5, 0.89),
                            position = "dodge",
                            color = "black",
                            slab_alpha = 0.5) +
  geom_vline(xintercept = 0) +
  facet_grid(name.full ~ .,
             scales = "free",
             switch="both") +
  viridis::scale_fill_viridis(option = "magma",
                              discrete = TRUE,
                              begin = 0.2,
                              end = 0.9) +
  guides(color = guide_legend(reverse = TRUE),
         fill = guide_legend(reverse = TRUE)) +
  theme_flynn(base_size = 11, base_family = "oswald") +
  theme(strip.text.y.left = element_text(size = 8, angle = 0, hjust = 0),
        axis.text.y = element_blank(),
        axis.ticks.y.left = element_blank()) +
  labs(x = "Estimate",
       y = "Coefficient",
       title = "Nested")

coef.plot.nested

ggsave(here::here("Figures/coefficient-plot-nested.png"),
       width = 7.5,
       height = 8.5,
       unit = "in")


```


```{r coef-plots-combined}

coef.plot.df.combined <- coef.plot.df.base |> 
  bind_rows(coef.plot.df.nested, 
            .id = "Model") |> 
  dplyr::mutate(Model = case_when(
    Model == 1 ~ "Base",
    TRUE ~ "Nested"
  ))


coef.plot.combined <- ggplot(coef.plot.df.combined, aes(y = reorder(name.full, -as.numeric(name.full)), x = value, color = `Model Group`, fill = `Model Group`)) +
  ggdist::stat_slabinterval(.width = c(0.5, 0.89),
                            position = "dodge",
                            color = "black",
                            slab_alpha = 0.5) +
  geom_vline(xintercept = 0) +
  facet_grid(name.full ~ Model,
             scales = "free",
             switch = "y") +
  viridis::scale_fill_viridis(option = "magma",
                              discrete = TRUE,
                              begin = 0.2,
                              end = 0.9) +
  guides(color = guide_legend(reverse = TRUE),
         fill = guide_legend(reverse = TRUE)) +
  theme_flynn(base_size = 11, base_family = "oswald") +
  theme(strip.text.y.left = element_text(size = 8, angle = 0, hjust = 0),
        axis.text.y = element_blank(),
        axis.ticks.y.left = element_blank()) +
  labs(x = "Estimate",
       y = "Coefficient")

coef.plot.combined


ggsave(here::here("Figures/coefficients-plot-combined.png"),
       width = 10,
       height = 9,
       unit = "in")

```


### PD Table


```{r pd-table}
### Also calculate pd for different variable groups
### 
pd.df.combined <- coef.plot.df.combined |> 
  dplyr::group_by(Model, name, `Model Group`) |> 
  dplyr::summarise(pd = bayestestR::pd(value))


```



### Separation Plots

```{r separation-plots-base}

# Set seed
set.seed(66502)



# Set model list
mod.list <- list("Intercepts" = model.intercepts.l1,
                 "Economic" = model.econ.l1,
                 "Political" = model.political.l1,
                 "Need" = model.need.l1,
                 "Combined" = model.combined.l1,
                 "Full" = model.full.l1)


# Generate 500 posterior draws of the expected value (i.e. 0 or 1)
# The posterior_predict function generates a matrix with columns representing individual cases rather than rows. 
# Need to convert columns to rows using the t() function.
# Use map() function to run over all of the models in mod.list (see above)

posterior.list <- map(.x = seq_along(mod.list), 
                      .f = ~ t(brms::posterior_epred(mod.list[[.x]], 
                                                     ndraws = 500,
                                                     re_formula = NULL)) |> 
                       as.data.frame() |> 
                       rowwise() |> 
                       dplyr::mutate(posterior_mean = mean(c_across(everything()))) |> 
                       bind_cols(mod.list[[.x]]$data) |> 
                        dplyr::mutate(predicted_deployment = case_when(posterior_mean > 0.17 ~ 1, 
                                                                       TRUE ~ 0)
                                      ) 
                      )
                      
# Combine the separate list elements into a single data frame. 
# Use the idcol argument to identify the separate models from the list elements.
sep.plot.data <- data.table::rbindlist(posterior.list, idcol = TRUE, fill = TRUE) |> 
  dplyr::mutate(.id = case_when(.id == 1 ~ "Intercepts",
                               .id == 2 ~ "Economic",
                               .id == 3 ~ "Political",
                               .id == 4 ~ "Need",
                               .id == 5 ~ "Combined",
                               .id == 6 ~ "Full"),
                .id = factor(.id,
                             levels = c("Intercepts", "Economic", "Political", "Need", "Combined", "Full"))) |> 
  group_by(.id) |>
  arrange(posterior_mean) |> 
  dplyr::mutate(index = row_number()) |> 
  pivot_longer(cols = c("V1":"V500"))



# Plot the separation plot
sep.plot.base <- ggplot() +
  geom_rect(data = sep.plot.data |> filter(deployment_lead_1 == 0), aes(x = index, xmin = index-0.5, xmax = index+0.5, y = posterior_mean, ymin=0, ymax = 1), fill = "gray95", show.legend = FALSE, alpha = 1, ) +
    geom_rect(data = sep.plot.data |> filter(deployment_lead_1 == 1), aes(x = index, xmin = index-0.5, xmax = index+0.5, y = posterior_mean, ymin=0, ymax = 1), fill = "black", show.legend = FALSE, alpha = 1, ) +
  stat_lineribbon(data = sep.plot.data, aes(x = index, y = value), .width = ppoints(50), show.legend = FALSE, alpha = 0.6) +
  #geom_line(data = sep.plot.data, aes(x = index, y = posterior_mean), color = "red") +
  facet_wrap(. ~ .id,
             scales = "free_x",
             ncol = 1) +
  theme_flynn(base_family = "oswald", base_size = 10) +
  viridis::scale_fill_viridis(option = "plasma",
                              begin = 0,
                              end = 1.0,
                              discrete = TRUE,
                              direction = -1)  +
  scale_x_continuous(breaks = scales::pretty_breaks(n = 10),
                     expand = c(0,0)) +
  scale_y_continuous(expand = c(0,0), limits = c(0,1)) +
  labs(x = "Index",
       y = "Predicted Probability",
       title = "Base")

sep.plot.base

ggsave(here::here("Figures/separation_plot_base.png"), 
       width = 6, 
       height = 7, 
       dpi = 400)



```




```{r separation-plots-nested}

# Set seed
set.seed(66502)


# Set model list
mod.list <- list("Intercepts" = model.intercepts.nested.l1,
                 "Economic" = model.econ.nested.l1,
                 "Political" = model.political.nested.l1,
                 "Need" = model.need.nested.l1,
                 "Combined" = model.combined.nested.l1,
                 "Full" = model.full.nested.l1)

# Generate 500 posterior draws of the expected value (i.e. 0 or 1)
# The posterior_predict function generates a matrix with columns representing individual cases rather than rows. 
# Need to convert columns to rows using the t() function.
# Use map() function to run over all of the models in mod.list (see above)

posterior.list <- map(.x = seq_along(mod.list), 
                      .f = ~ t(brms::posterior_epred(mod.list[[.x]], 
                                                     ndraws = 500,
                                                     re_formula = NULL)) |> 
                       as.data.frame() |> 
                       rowwise() |> 
                       dplyr::mutate(posterior_mean = mean(c_across(everything()))) |> 
                       bind_cols(mod.list[[.x]]$data) |> 
                        dplyr::mutate(predicted_deployment = case_when(posterior_mean > 0.17 ~ 1, 
                                                                       TRUE ~ 0)
                                      ) 
                      )
                      
# Combine the separate list elements into a single data frame. 
# Use the idcol argument to identify the separate models from the list elements.
sep.plot.data <- data.table::rbindlist(posterior.list, idcol = TRUE, fill = TRUE) |> 
  dplyr::mutate(.id = case_when(.id == 1 ~ "Intercepts",
                               .id == 2 ~ "Economic",
                               .id == 3 ~ "Political",
                               .id == 4 ~ "Need",
                               .id == 5 ~ "Combined",
                               .id == 6 ~ "Full"),
                .id = factor(.id,
                             levels = c("Intercepts", "Economic", "Political", "Need", "Combined", "Full"))) |> 
  group_by(.id) |>
  arrange(posterior_mean) |> 
  dplyr::mutate(index = row_number()) |> 
  pivot_longer(cols = c("V1":"V500"))



# Plot the separation plot
sep.plot.nested <- ggplot() +
  geom_rect(data = sep.plot.data |> filter(deployment_lead_1 == 0), aes(x = index, xmin = index-0.5, xmax = index+0.5, y = posterior_mean, ymin=0, ymax = 1), fill = "gray95", show.legend = FALSE, alpha = 1, ) +
    geom_rect(data = sep.plot.data |> filter(deployment_lead_1 == 1), aes(x = index, xmin = index-0.5, xmax = index+0.5, y = posterior_mean, ymin=0, ymax = 1), fill = "black", show.legend = FALSE, alpha = 1, ) +
  stat_lineribbon(data = sep.plot.data, aes(x = index, y = value), .width = ppoints(50), show.legend = FALSE, alpha = 0.6) +
  #geom_line(data = sep.plot.data, aes(x = index, y = posterior_mean), color = "red") +
  facet_wrap(. ~ .id,
             scales = "free_x",
             ncol = 1) +
  theme_flynn(base_family = "oswald", base_size = 10) +
  viridis::scale_fill_viridis(option = "plasma",
                              begin = 0,
                              end = 1.0,
                              discrete = TRUE,
                              direction = -1)  +
  scale_x_continuous(expand = c(0,0),
                     breaks = scales::pretty_breaks(n = 5)) +
  scale_y_continuous(expand = c(0,0), limits = c(0,1)) +
  labs(x = "Index",
       y = "Predicted Probability",
       title = "Nested")

sep.plot.nested

ggsave(here::here("Figures/separation_plot_nested.png"), 
       width = 6, 
       height = 6, 
       dpi = 400)


```



#### Trial Statistic

```{r trial statistic}

cumulative.predictions <- sep.plot.data |> 
  group_by(.id) |> 
  arrange(posterior_mean) |> 
  dplyr::mutate(cumulative_deployments = cumsum(deployment_lead_1),
                cumulative_deployments_prop = cumulative_deployments/max(cumulative_deployments),
                curve = (cumulative_deployments_prop - posterior_mean) / (cumulative_deployments_prop + posterior_mean),
                index_rate = index/max(index)) |> 
  ungroup()

ggplot(cumulative.predictions) +
  geom_line( aes(x = index, y = cumulative_deployments_prop)) +
  geom_line(aes(x = index, y = posterior_mean), color = "red") +
  facet_wrap(~ .id,
             ncol = 1)



ggplot(cumulative.predictions) +
  geom_line( aes(x = cumulative_deployments_prop, y = posterior_mean)) +
  facet_wrap(~ .id,
             ncol = 1)

```



```{r sep-plot-combined}

wrap_plots(sep.plot.base, sep.plot.nested) +
  plot_layout(guides = "collect")

ggsave(here::here("Figures/separation_plot_combined.png"),
       width = 8,
       height = 7,
       dpi = 400)

```



### ICC Plot

```{r icc-plot}

set.seed(66502)

model <- model.full.l1


sd <- VarCorr(model)$countryname$sd[[1]]

fixed <- fixef(model)

fixed_sum <- sum(fixed[,1])

M <- 1000

Uoj <- rnorm(M, 0, sd)

logit_p_hat <- fixed_sum + Uoj

p_hat <- exp(logit_p_hat) / (1 + exp(logit_p_hat))

var_L1 <- p_hat * (1 - p_hat)

sigma2 <- mean(var_L1)

simICC <- var(p_hat) / (var(p_hat) + sigma2)

simICC



```





### ROC Curve Plots

```{r roc-curves-base}
# Set Seed
set.seed(66502)


# Set model list
mod.list <- list("Intercepts" = model.intercepts.l1,
                 "Economic" = model.econ.l1,
                 "Political" = model.political.l1,
                 "Need" = model.need.l1,
                 "Combined" = model.combined.l1,
                 "Full" = model.full.l1)

# Generate 100 posterior draws of the expected value (i.e. 0 or 1)
# The posterior_epred function generates a matrix with columns representing individual cases rather than rows. 
# Need to convert columns to rows using the t() function.
# Use map() function to run over all of the models in mod.list (see above)

posterior.list.base <- map(.x = seq_along(mod.list), 
                       .f = ~ t(brms::posterior_epred(mod.list[[.x]], 
                                                      ndraws = 200,
                                                      re_fomula = NULL)) |> 
                         as.data.frame() |> 
                         rowwise() |> 
                         dplyr::mutate(posterior_mean = mean(c_across(everything()))) |> 
                         bind_cols(mod.list[[.x]]$data) |> 
                        mutate(probs = list(seq(0.01, 1.0, 0.01)))
                      )

roc.df.base <- data.table::rbindlist(posterior.list.base, 
                                idcol = TRUE, 
                                fill = TRUE) |> 
  dplyr::mutate(.id = case_when(.id == 1 ~ "Intercepts",
                               .id == 2 ~ "Economic",
                               .id == 3 ~ "Political",
                               .id == 4 ~ "Need",
                               .id == 5 ~ "Combined",
                               .id == 6 ~ "Full"),
                .id = factor(.id,
                             levels = c("Full", "Combined", "Need", "Political", "Economic", "Intercepts"))) |> 
  group_by(.id) |>
  arrange(posterior_mean) |> 
  dplyr::mutate(index = row_number()) |> 
  pivot_longer(cols = c("V1":"V100")) |> 
  unnest(probs) |> 
  dplyr::mutate(predicted_deployment = case_when(value > probs ~ 1, 
                                                 TRUE ~ 0),
                true_positive = case_when(deployment_lead_1 == 1 & predicted_deployment == 1 ~ 1,
                                          TRUE ~ 0),
                false_positive = case_when(deployment_lead_1 == 0 & predicted_deployment == 1 ~ 1,
                                           TRUE ~ 0),
                true_negative = case_when(deployment_lead_1 == 0 & predicted_deployment == 0 ~ 1,
                                          TRUE ~ 0),
                false_negative = case_when(deployment_lead_1 == 1 & predicted_deployment == 0 ~ 1,
                                           TRUE ~ 0)) |> 
  group_by(.id, probs) |>
  dplyr::mutate(sensitivity = sum(true_positive)/(sum(true_positive) + sum(false_negative)),
                specificity = sum(true_negative)/(sum(true_negative) + sum(false_positive)),
                precision = sum(true_positive)/(sum(true_positive) + sum(false_positive)),
                recall = sum(true_positive)/(sum(true_positive) + sum(false_negative)),
                accuracy = (sum(true_positive) + sum(true_negative)) / (sum(true_positive) + sum(true_negative) + sum(false_positive) + sum(false_negative))) |> 
  dplyr::summarise(sensitivity = mean(sensitivity),
                   specificity = mean(specificity),
                   precision = mean(precision),
                   recall = mean(recall),
                   accuracy = mean(accuracy))


roc.base <- ggplot(roc.df.base, aes(x = 1 - specificity, y = sensitivity, color = .id, linetype = .id)) +
  geom_line(linewidth = 0.7) +
  geom_abline(intercept = 0, slope = 1, linetype = "dashed") +
  theme_flynn(base_family = "oswald", base_size = 10) +
  coord_fixed(ratio = 1) +
  labs(x = "False Positive Rate",
       y = "True Positive Rate",
       title = "ROC Curves for Base Models") +
  viridis::scale_color_viridis(option = "turbo",
                               discrete = TRUE) +
  scale_x_continuous(expand = c(0,0), limits = c(0,1.01)) +
  scale_y_continuous(expand = c(0,0), limits = c(0,1.01)) +
  theme(legend.position = "bottom",
        legend.title = element_text(margin = margin(r = 0.2, unit = "cm"))) +
  labs(color = "Model",
       linetype = "Model")

ggsave(here::here("Figures/roc_curves_base.png"), width = 7, height = 6, dpi = 400)

```





```{r roc-curves-nested}

# Set seed
set.seed(66502)

# Set model list
mod.list <- list("Intercepts" = model.intercepts.nested.l1,
                 "Economic" = model.econ.nested.l1,
                 "Political" = model.political.nested.l1,
                 "Need" = model.need.nested.l1,
                 "Combined" = model.combined.nested.l1,
                 "Full" = model.full.nested.l1)

# Generate 500 posterior draws of the expected value (i.e. 0 or 1)
# The posterior_predict function generates a matrix with columns representing individual cases rather than rows. 
# Need to convert columns to rows using the t() function.
# Use map() function to run over all of the models in mod.list (see above)

posterior.list.nested <- map(.x = seq_along(mod.list), 
                       .f = ~ t(brms::posterior_epred(mod.list[[.x]], 
                                                      ndraws = 200,
                                                      re_formula = NULL)) |> 
                         as.data.frame() |> 
                         rowwise() |> 
                         dplyr::mutate(posterior_mean = mean(c_across(everything()))) |> 
                         bind_cols(mod.list[[.x]]$data) |> 
                        mutate(probs = list(seq(0.01,1.0, 0.005)))
                      )

roc.df.nested <- data.table::rbindlist(posterior.list.nested, idcol = TRUE, fill = TRUE) |> 
  dplyr::mutate(.id = case_when(.id == 1 ~ "Intercepts",
                               .id == 2 ~ "Economic",
                               .id == 3 ~ "Political",
                               .id == 4 ~ "Need",
                               .id == 5 ~ "Combined",
                               .id == 6 ~ "Full"),
                .id = factor(.id,
                             levels = c("Full", "Combined", "Need", "Political", "Economic", "Intercepts"))) |> 
  group_by(.id) |>
  arrange(posterior_mean) |> 
  dplyr::mutate(index = row_number()) |> 
  pivot_longer(cols = c("V1":"V100")) |> 
  unnest(probs) |> 
  dplyr::mutate(predicted_deployment = case_when(value > probs ~ 1, 
                                                 TRUE ~ 0),
                true_positive = case_when(deployment_lead_1 == 1 & predicted_deployment == 1 ~ 1,
                                          TRUE ~ 0),
                false_positive = case_when(deployment_lead_1 == 0 & predicted_deployment == 1 ~ 1,
                                           TRUE ~ 0),
                true_negative = case_when(deployment_lead_1 == 0 & predicted_deployment == 0 ~ 1,
                                          TRUE ~ 0),
                false_negative = case_when(deployment_lead_1 == 1 & predicted_deployment == 0 ~ 1,
                                           TRUE ~ 0)) |> 
  group_by(.id, probs) |>
  dplyr::mutate(sensitivity = sum(true_positive)/(sum(true_positive) + sum(false_negative)),
                specificity = sum(true_negative)/(sum(true_negative) + sum(false_positive)),
                precision = sum(true_positive)/(sum(true_positive) + sum(false_positive)),
                recall = sum(true_positive)/(sum(true_positive) + sum(false_negative)),
                accuracy = (sum(true_positive) + sum(true_negative)) / (sum(true_positive) + sum(true_negative) + sum(false_positive) + sum(false_negative))) |> 
  dplyr::summarise(sensitivity = mean(sensitivity),
                   specificity = mean(specificity),
                   precision = mean(precision),
                   recall = mean(recall),
                   accuracy = mean(accuracy))


roc.nested <- ggplot(roc.df.nested, aes(x = 1 - specificity, y = sensitivity, color = .id, linetype = .id)) +
  geom_line(linewidth = 0.7) +
  geom_abline(intercept = 0, slope = 1, linetype = "dashed") +
  theme_flynn(base_family = "oswald", base_size = 10) +
  coord_fixed(ratio = 1) +
  labs(x = "False Positive Rate",
       y = "True Positive Rate",
       title = "ROC Curves for Nested Models") +
  viridis::scale_color_viridis(option = "turbo",
                               discrete = TRUE) +
  scale_x_continuous(expand = c(0,0), limits = c(0,1.01)) +
  scale_y_continuous(expand = c(0,0), limits = c(0,1.01)) +
  theme(legend.position = "bottom",
        legend.title = element_text(margin = margin(r = 0.2, unit = "cm"))) +
  labs(color = "Model",
       linetype = "Model")

ggsave(here::here("Figures/roc_curves_nested.png"), width = 7, height = 6, dpi = 400)

```


```{r roc-plots-combined}

wrap_plots(roc.base, roc.nested) +
  plot_layout(guides = "collect") &
  theme(legend.position = "bottom",
        plot.margin = margin(b = -1, unit = "cm"))

ggsave(here::here("Figures/roc_curves_combined.png"), 
       width = 10, 
       height = 7, 
       dpi = 400)


```



### Accuracy Table

```{r sensitivity-specificity}

class.summary <- roc.df.base |> 
  bind_rows(roc.df.nested,
            .id = "Nesting") |> 
  dplyr::mutate(Nesting = case_when(
    Nesting == 1 ~ "Base",
    TRUE ~ "Nested"
  )) |> 
  dplyr::filter(probs == 0.17) |> 
  dplyr::select(
    "Nesting" = 1,
    "Model" = 2,
    "Probability\nThreshold" = 3,
    "Sensitivity" = 4,
    "Specificity" = 5,
    "Precision" = 6,
    "Recall" = 7,
    "Accuracy" = 8
  ) |> 
  dplyr::select(!c(Recall, Precision)) |> 
  dplyr::mutate(across(c(3:5),
                ~round(.x, 3))) |> 
  tt(caption = "Predictive accuracy by model and nesting group. \\label{tab:accuracytab}",
     width = c(0.15, 0.15, 0.15, 0.15, 0.15, 0.15),
     notes = "The probability threshold represents the probability cutpoint at which predictions are classified as 'positive' or 'negative' observations. That is, whether a an observation is predicted to have a deployment or no deployment. Observations with a predicted probability equal to or greater than the probability threshold are classified as having a deployment, while those that are less than the threshold value are classified as not having a deployment.") |> 
  style_tt(fontsize = 0.8) |> 
  style_tt(i = "notes",
           fontsize = 0.6) |> 
  style_tt(
    i = 0,
    j = c(1:6),
    bold = TRUE,
    alignv = "b"
  ) |> 
  style_tt(i = 6,
           line = "b",
           line_color = "black",
           line_width = 0.05) |>
  theme_striped() |>
  tt_save(here::here("Tables/acc_tab.tex"),
          overwrite = TRUE)


```




### ROC AUC

```{r}


roc.auc <- roc.df.base |> 
  bind_rows(roc.df.nested,
            .id = "Nesting") |> 
  dplyr::mutate(Nesting = case_when(
    Nesting == 1 ~ "Base",
    TRUE ~ "Nested"
  )) |> 
  dplyr::group_by(Nesting, .id) |> 
  dplyr::summarise(auc = pracma::trapz(specificity, sensitivity)) |> 
  dplyr::select(
    `Nesting` = 1,
    `Model` = 2,
    `AUC` = 3
  ) |> 
  dplyr::mutate(across(2,
                ~round(.x, 3))) |> 
  tt(caption = "Area under the curve (AUC) for ROC curve plots. \\label{tab:auctab}",
     width = c(0.20, 0.20, 0.20),
     notes = "Area under the curve (AUC) values show the probability that the model, if given a pair of randomly selected deployment and non-deployment examples, will estimate a higher predicted probability of a deployment to the actual deployment case than the non-deployment case.") |> 
  style_tt(fontsize = 0.9) |> 
  style_tt(j = 3,
           align = "r") |> 
  style_tt(i = "notes",
           fontsize = 0.6) |> 
  style_tt(
    i = 0,
    j = c(1:3),
    bold = TRUE,
    alignv = "b"
  ) |> 
  style_tt(i = 6,
           line = "b",
           line_color = "black",
           line_width = 0.05) |>
  theme_striped() |>
  tt_save(here::here("Tables/auc_tab.tex"),
          overwrite = TRUE)



```





### Model Fit Checks

```{r looic-checks}

# Create list of model objects
mod.list <- list("Intercepts" = model.intercepts.l1,
                 "Economic" = model.econ.l1,
                 "Political" = model.political.l1,
                 "Need" = model.need.l1,
                 "Combined" = model.combined.l1,
                 "Full" = model.full.l1)




# Run LOO on all five models and extract pointwise estimates

loo.out <- mod.list |> 
  imap(\(model, modelname) {
    loo(model, pointwise = F)$pointwise |> 
      as.data.frame() |> 
      mutate(name = modelname)
  }) |> 
  purrr::list_rbind()

# Combine loo estimtes with sample data
loo.out.insample <- mod.list |> 
  imap(\(model, modelname) {
    loo(model, 
        pointwise = F)$pointwise |> 
      as.data.frame() |> 
      dplyr::mutate(row_index = row_number(),
                    modelname = modelname) |> 
      left_join(data.analysis |> dplyr::select(countryname, year, row_index)
                , by = "row_index")
  }) |> 
  purrr::list_rbind() |> 
  dplyr::mutate(modelname = factor(modelname,
                                   levels = c("Full", "Combined", "Political", "Economic", "Need", "Intercepts")))



ggplot(data = loo.out.insample,
       aes(x = row_index, y = influence_pareto_k)) +
  geom_point(shape = 3) +
  geom_label_repel(data = loo.out.insample |> filter(abs(influence_pareto_k) > 0.5),
                   aes(label = glue::glue("{countryname}, {year}")),
                   size = 1) +
  geom_hline(yintercept = 0) +
  theme_flynn(base_family = "oswald",
              base_size = 9) +
  facet_wrap(. ~ modelname,
             nrow = 1) +
  labs(title = "Base Models",
       y = "Pareto k Influence Values",
       x = "Index")

ggsave(here::here("Figures/loo_base_model_fit.png"),
       height = 5,
       width = 8,
       unit = "in")







## Now for nested models
# Create list of model objects
mod.list <- list("Intercepts" = model.intercepts.nested.l1,
                 "Economic" = model.econ.nested.l1,
                 "Political" = model.political.nested.l1,
                 "Need" = model.need.nested.l1,
                 "Combined" = model.combined.nested.l1,
                 "Full" = model.full.nested.l1)




# Run LOO on all five models and extract pointwise estimates

loo.out <- mod.list |> 
  imap(\(model, modelname) {
    loo(model, pointwise = F)$pointwise |> 
      as.data.frame() |> 
      mutate(name = modelname)
  }) |> 
  purrr::list_rbind()

# Combine loo estimtes with sample data
loo.out.insample <- mod.list |> 
  imap(\(model, modelname) {
    loo(model, 
        pointwise = F)$pointwise |> 
      as.data.frame() |> 
      dplyr::mutate(row_index = row_number(),
                    modelname = modelname) |> 
      left_join(data.analysis.nested |> dplyr::select(countryname, year, row_index)
                , by = "row_index")
  }) |> 
  purrr::list_rbind() |> 
  dplyr::mutate(modelname = factor(modelname,
                                   levels = c("Full", "Combined", "Political", "Economic", "Need", "Intercepts")))



ggplot(data = loo.out.insample,
       aes(x = row_index, y = influence_pareto_k)) +
  geom_point(shape = 3) +
  geom_label_repel(data = loo.out.insample |> filter(abs(influence_pareto_k) > 0.5),
                   aes(label = glue::glue("{countryname}, {year}")),
                   size = 1) +
  geom_hline(yintercept = 0) +
  theme_flynn(base_family = "oswald",
              base_size = 9) +
  facet_wrap(. ~ modelname,
             nrow = 1) +
  labs(title = "Nested Models",
       y = "Pareto k Influence Values",
       x = "Index")

ggsave(here::here("Figures/loo_nested_model_fit.png"),
       height = 5,
       width = 8,
       unit = "in")

```



### K Fold cross validation

```{r}

# Set up future package specifications
plan(multisession, 
     workers = 4)

kfold.out <- brms::kfold(model.intercepts.nested.l1,
                         model.econ.nested.l1, 
                         model.political.nested.l1,
                         model.need.nested.l1,
                         model.combined.nested.l1,
                         model.full.nested.l1,
                         K = 10,
                         folds = "grouped",
                         group = "countryname",
                         compare = TRUE,
                         save_fits = TRUE)


```



```{r loo-table-pareto-k}
#| echo: false
#| message: false

set.seed(66502)

# ============================================================================
# 1. Comparison table: ELPD and probability worse
# ===========================================================================
# 
# 

loo.nested.out <- loo::loo(model.intercepts.nested.l1,
                           model.econ.nested.l1,
                           model.political.nested.l1,
                           model.need.nested.l1,
                           model.combined.nested.l1,
                           model.full.nested.l1,
                           pointwise = FALSE)

loo.diffs.raw <- as.data.frame(loo.nested.out$diffs)

# brms stores model names as rownames and does not carry a p_worse column;
# these two guards make the chunk work either way.
if (!"model" %in% names(loo.diffs.raw)) {
  loo.diffs.raw <- tibble::rownames_to_column(loo.diffs.raw, var = "model")
}

if (!"p_worse" %in% names(loo.diffs.raw)) {
  loo.diffs.raw <- loo.diffs.raw |>
    dplyr::mutate(
      p_worse = dplyr::if_else(se_diff == 0, NA_real_, pnorm(elpd_diff / se_diff))
    )
}

loo.tab.df <- loo.diffs.raw |>
  dplyr::mutate(
    model = dplyr::case_when(
      stringr::str_detect(model, "intercept") ~ "Intercepts",
      stringr::str_detect(model, "full")      ~ "Full",
      stringr::str_detect(model, "combined")  ~ "Combined",
      stringr::str_detect(model, "political") ~ "Political",
      stringr::str_detect(model, "need")      ~ "Need",
      stringr::str_detect(model, "econ")      ~ "Economic",
      TRUE ~ model
    ),
    dplyr::across(c(elpd_loo, se_elpd_loo, elpd_diff, se_diff), ~ round(.x, 1)),
    p_worse = round(p_worse, 2)
  ) |>
  dplyr::select(model, elpd_loo, se_elpd_loo, elpd_diff, se_diff, p_worse) |>
  dplyr::rename(
    "Model"                = 1,
    "ELPD"                 = 2,
    "Std. Err."            = 3,
    "ELPD Diff."           = 4,
    "ELPD Diff. Std. Err." = 5,
    "Prob. Worse"          = 6
  )

# LaTeX table
loo.tab.out <- loo.tab.df |>
  tt(caption = "Leave-one-out cross-validation comparison of nested models. \\label{tab:lootabnested}",
     notes = "ELPD is the expected log pointwise predictive density estimated by PSIS-LOO; higher values indicate better out-of-sample predictive performance. Differences are calculated relative to the best-fitting model, which is therefore fixed at zero and has no probability worse value. Probability worse gives the normal-approximation probability that the model in that row has lower expected predictive accuracy than the best-fitting model.") |>
  style_tt(fontsize = 0.8) |>
  style_tt(i = "notes", fontsize = 0.6) |>
  style_tt(i = 0, j = c(1:6), bold = TRUE, alignv = "b") |>
  theme_striped() |>
  save_tt(here::here("Tables/loo_tab_nested.tex"), overwrite = TRUE)


# ============================================================================
# 2. Pareto k diagnostics from the precomputed loo objects
# ============================================================================
# Read $diagnostics directly rather than calling loo(..., pointwise = TRUE),
# which the gp() term in the full model does not support.

pareto.k.df <- loo.nested.out[["loos"]] |>
  purrr::imap(\(loo.obj, modelname) {
    tibble::tibble(
      model      = modelname,
      row_index  = seq_along(loo.obj[["diagnostics"]][["pareto_k"]]),
      pareto_k   = loo.obj[["diagnostics"]][["pareto_k"]],
      psis_n_eff = loo.obj[["diagnostics"]][["n_eff"]]
    )
  }) |>
  purrr::list_rbind() |>
  dplyr::mutate(
    model = dplyr::case_when(
      stringr::str_detect(model, "intercept") ~ "Intercepts",
      stringr::str_detect(model, "full")      ~ "Full",
      stringr::str_detect(model, "combined")  ~ "Combined",
      stringr::str_detect(model, "political") ~ "Political",
      stringr::str_detect(model, "need")      ~ "Need",
      stringr::str_detect(model, "econ")      ~ "Economic",
      TRUE ~ model
    ),
    # Same row order as the table, best-fitting model on top
    model = factor(model, levels = rev(loo.tab.df$Model))
  ) |>
  dplyr::left_join(
    data.analysis.nested |> dplyr::select(row_index, countryname, year),
    by = "row_index"
  )

# Observations to label: anything above the 0.7 reliability threshold. If a
# model has none, fall back to its three most influential country-years so
# every row still carries some annotation.
pareto.k.labels <- pareto.k.df |>
  dplyr::filter(pareto_k > 0.7)

if (nrow(pareto.k.labels) == 0) {
  pareto.k.labels <- pareto.k.df |>
    dplyr::slice_max(pareto_k, n = 3, by = model)
}


# ============================================================================
# 3. Figure: distribution of Pareto k values
# ============================================================================

pareto.k.plot <- ggplot(pareto.k.df,
                        aes(x = pareto_k, y = model, fill = model)) +
  geom_vline(xintercept = c(0.5, 0.7),
             linetype   = c("dotted", "dashed"),
             linewidth  = 0.3) +
  ggdist::stat_slab(alpha       = 0.6,
                    normalize   = "groups",
                    height      = 0.7,
                    show.legend = FALSE) +
  geom_point(shape       = 3,
             size        = 0.5,
             alpha       = 0.35,
             position    = position_nudge(y = -0.12),
             show.legend = FALSE) +
  ggrepel::geom_label_repel(
    data          = pareto.k.labels,
    aes(label = glue::glue("{countryname}, {year}")),
    fill              = "white",
    size              = 1.7,
    family            = "oswald",
    label.padding     = unit(0.10, "lines"),
    label.size        = 0.20,
    nudge_y           = -0.38,
    direction         = "y",
    segment.size      = 0.15,
    segment.alpha     = 0.6,
    min.segment.length = 0,
    max.overlaps      = 20,
    show.legend       = FALSE
  ) +
  viridis::scale_fill_viridis(option   = "magma",
                              discrete = TRUE,
                              begin    = 0.2,
                              end      = 0.9) +
  scale_x_continuous(breaks = scales::pretty_breaks(n = 6)) +
  scale_y_discrete(expand = expansion(add = c(0.85, 0.6))) +
  theme_flynn(base_size = 11, base_family = "oswald") +
  labs(x        = "Pareto k",
       y        = NULL,
       title    = "PSIS-LOO Diagnostics and Model Comparison",
       subtitle = "Dotted line marks k = 0.5, dashed line k = 0.7. Values above 0.7 indicate observations for which the importance sampling estimate is unreliable.")


# ============================================================================
# 4. Table grob and side-by-side layout
# ============================================================================

tab.theme <- gridExtra::ttheme_minimal(
  base_size   = 12,
  base_family = "oswald",
  core    = list(fg_params = list(hjust = 1, x = 0.95),
                 bg_params = list(fill = c("white", "gray95"))),
  colhead = list(fg_params = list(fontface = "bold", hjust = 0.5, x = 0.5))
)

loo.tab.grob <- gridExtra::tableGrob(
  loo.tab.df |>
    dplyr::select(Model, ELPD, `ELPD Diff.`, `Prob. Worse`) |>
    dplyr::rename("ELPD\nDiff." = "ELPD Diff.",
                  "Prob.\nWorse" = "Prob. Worse"),
  rows  = NULL,
  theme = tab.theme
)

pareto.k.combined <- pareto.k.plot +
  patchwork::wrap_elements(full = loo.tab.grob) +
  patchwork::plot_layout(widths = c(1, 1))

pareto.k.combined

ggsave(here::here("Figures/pareto_k_nested.png"),
       plot   = pareto.k.combined,
       width  = 10,
       height = 5.5,
       dpi    = 400)
```



# Posterior Analysis

### Posterior Predictive Checks

```{r}

# Base models

mod.list <- list("Intercepts" = model.intercepts.l1,
                 "Economic" = model.econ.l1,
                 "Political" = model.political.l1,
                 "Need" = model.need.l1,
                 "Combined" = model.combined.l1,
                 "Full" = model.full.l1)


base.model.pp.check <- purrr::imap(
  .x = mod.list,
  .f = ~ brms::pp_check(.x,
                        ndraws = 200,
                        type = "bars") + 
    labs(title = glue::glue("{.y}")) + 
    theme_flynn()
)

ppcheck.plots <- patchwork::wrap_plots(base.model.pp.check) +
  plot_layout(guides = "collect")

ggsave(here::here("Figures/pp_check_plots_base.png"),
       height = 7, 
       width = 9,
       unit = "in")



# Now for nested models

mod.list <- list("Intercepts" = model.intercepts.nested.l1,
                 "Economic" = model.econ.nested.l1,
                 "Political" = model.political.nested.l1,
                 "Need" = model.need.nested.l1,
                 "Combined" = model.combined.nested.l1,
                 "Full" = model.full.nested.l1)


nested.model.pp.check <- purrr::imap(
  .x = mod.list,
  .f = ~ brms::pp_check(.x,
                        ndraws = 200,
                        type = "bars") + 
    labs(title = glue::glue("{.y}")) + 
    theme_flynn()
)

ppcheck.plots <- patchwork::wrap_plots(nested.model.pp.check) +
  plot_layout(guides = "collect")

ggsave(here::here("Figures/pp_check_plots_nested.png"),
       height = 7, 
       width = 9,
       unit = "in")


```



### Chain Analysis

```{r}

# Base models
# 
# Establish model list
mod.list <- list("Intercepts" = model.intercepts.l1,
                 "Economic" = model.econ.l1,
                 "Political" = model.political.l1,
                 "Need" = model.need.l1,
                 "Combined" = model.combined.l1,
                 "Full" = model.full.l1)


# Get MCMC chain density figures for each model
base.model.chains <- purrr::imap(
  .x = mod.list,
  .f = ~ brms::mcmc_plot(.x,
                         type = "dens_overlay") + 
    labs(title = glue::glue("{.y}")) + 
    theme_flynn(base_size = 9)
)


# Save each list item as a separate image file
purrr::imap(
  .x = base.model.chains,
  .f = ~ ggsave(here::here(glue::glue("Figures/mcmc_plot_base_model_{.y}.png")),
                plot = .x,
                height = 8,
                width = 9,
                unit = "in")
  )


# Now do it for nested models

# Establish model list
mod.list <- list("Intercepts" = model.intercepts.nested.l1,
                 "Economic" = model.econ.nested.l1,
                 "Political" = model.political.nested.l1,
                 "Need" = model.need.nested.l1,
                 "Combined" = model.combined.nested.l1,
                 "Full" = model.full.nested.l1)


# Get MCMC chain density figures for each model
nested.model.chains <- purrr::imap(
  .x = mod.list,
  .f = ~ brms::mcmc_plot(.x,
                         type = "dens_overlay") + 
    labs(title = glue::glue("{.y}")) + 
    theme_flynn(base_size = 9)
)


# Save each list item as a separate image file
purrr::imap(
  .x = nested.model.chains,
  .f = ~ ggsave(here::here(glue::glue("Figures/mcmc_plot_nested_model_{.y}.png")),
                plot = .x,
                height = 8,
                width = 9,
                unit = "in")
  )


```


### Rhat Plots

```{r}

# Base models
# 
mod.list <- list("Intercepts" = model.intercepts.l1,
                 "Economic" = model.econ.l1,
                 "Political" = model.political.l1,
                 "Need" = model.need.l1,
                 "Combined" = model.combined.l1,
                 "Full" = model.full.l1)


rhat.base <- imap(
  .x = mod.list,
  .f = ~ brms::mcmc_plot(.x,
                         type = "rhat") + 
    labs(title = glue::glue("{.y}")) + 
    theme_flynn(base_size = 9)
)

purrr::imap(
  .x = rhat.base,
  .f = ~ ggsave(here::here(glue::glue("Figures/rhat_plot_base_model_{.y}.png")),
                plot = .x,
                height = 8,
                width = 9,
                unit = "in")
  )



## Nested Models
## 
mod.list <- list("Intercepts" = model.intercepts.nested.l1,
                 "Economic" = model.econ.nested.l1,
                 "Political" = model.political.nested.l1,
                 "Need" = model.need.nested.l1,
                 "Combined" = model.combined.nested.l1,
                 "Full" = model.full.nested.l1)


rhat.base <- imap(
  .x = mod.list,
  .f = ~ brms::mcmc_plot(.x,
                         type = "rhat") + 
    labs(title = glue::glue("{.y}")) + 
    theme_flynn(base_size = 9)
)

purrr::imap(
  .x = rhat.base,
  .f = ~ ggsave(here::here(glue::glue("Figures/rhat_plot_nested_model_{.y}.png")),
                plot = .x,
                height = 8,
                width = 9,
                unit = "in")
  )

```


### Projection Prediction Assessment


```{r}

#refmod <- projpred::get_refmodel(model.full.l1)

#projections <- projpred::cv_varsel(refmod)

```
